\gettitle

### 2020-01-24 assignment6/submission6.tex
Added Task 2 solution

\section*{3 - Causal Mulitcast}

>>>>

\subsubsection*{i.}
False\\
m$_3$ is delivered to P$_$2 but not to P$_1$ and P$_3$ which are correct.
\subsubsection*{ii.}
True\\
m$_1$, m$_2$ and m$_4$ are send by correct processes and delivered exactly once by P$_1$ and P$_3$
\subsubsection*{iii.}
True\\
Only P$_1$ sends more than 1 messaage. The second one is send after all processes recieved the first one. So it is FIFO multicast.\\
P$_1$ and P$_2$ are delivering m$_1$ and m$_2$ in diffrent orders. So no atomic multicast.
\subsubsection*{iv.}
False\\
P$_2$ does not deliver m$_1$ but m$_4$, that violates Uniform FIFO.
\subsection*{b)}

\subsubsection*{i.}
Reliable Multicast: fullfilled\\
FIFO Multicast: violated\\
Causal Multicast: violated\\
Atomic Multicast: violated\\
\subsubsection*{ii.}
Reliable Multicast: violated\\
FIFO Multicast: violated\\
Causal Multicast: violated\\
Atomic Multicast: violated\\
\subsubsection*{iii.}
Reliable Multicast: fullfilled\\
FIFO Multicast: fullfilled\\
Causal Multicast: fullfilled\\
Atomic Multicast: violated\\
\section*{3 - Causal Mulitcast}
